Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/qualityattributes.tex
Adding section about SOA penalties

>>>>

Naturally this generality do not necesarrliy come free. A look-up in a database behind a service, especially a web-service, is far slower than a direct look-up in a local database, thereby influencing Performance poorly. On the other hand the use of web-services may increase Availability, as the functionality is deployed on multiple servers, thereby redusing the chance of the system becomming fully non-responsive. Naturally the critical path must be evaluated, as if a link on the critical path chain become non-responsive then the entire system becomes non-responsive.
